Done

### 2024-06-04 done.qmd
update

@@

>>>>

2024-01-03: BBC Future article [Tetris: How a US teenager achieved the 'impossible' and what his feat tells us about human capabilities](https://www.bbc.co.uk/future/article/20240103-tetris-how-a-us-teenager-achieved-the-impossible)

@@

2015 Data Scientist in Residence at [folksy.com](folksy.com). See [Folksy data analysis: buyer decision time](http://blog.folksy.com/2015/03/09/folksy-data-analysis-buyer-decision-time)
